### 2017-10-06 cv-body.tex
Fix broken links

package}, \href{https://github.com/ss3sim/ss3sim}{code},
\href{https://sean.updog.co/ss3sim-vignette.pdf}{vignette}).

@@

(\href{http://www.esajournals.org/doi/pdf/10.1890/13-0916.1}{PDF}).

@@

\url{https://doi.org/10.4033/iee.2013.6.9.n}
(\href{http://library.queensu.ca/ojs/index.php/IEE/article/download/4931/4899}{PDF}).

@@

(\href{http://icesjms.oxfordjournals.org/cgi/reprint/fss105?ijkey=pFRzMGEDycomI3X\&keytype=ref}{PDF}).

>>>>

package}, \href{https://github.com/ss3sim/ss3sim}{code}.

@@

(\href{http://onlinelibrary.wiley.com/doi/10.1890/13-0916.1/epdf}{PDF}).

@@

\url{https://doi.org/10.4033/iee.v6i1.4931} (Open access).

@@

(\href{https://sean.updog.co/Anderson_etal_2012_Assessing_global_marine_fishery.pdf}{PDF}).
